%--------------------------------------------------
\begin{frame}
\frametitle{Encryption for connexions : SSL/TLS}
\begin{itemize}
\item Session layer based, affect application layer (TFP, HTTP, SMTP, IMAP, POP
, DNS, RTMP ...)
\item Prefer using TLS over SSL when you have choice.
\item Asymetrical encryption, forward secrecy (Diffie-Hellman).
\end{itemize}

Only use up to date browser in order to have the correct fingerprint cached
on your computer and avoid MITM attack.
If your browser does not have a certificate pinning system install
certificate patrol (assuming your first connection is safe) or HTTPS everywhere
with the SSL observatory ON.
\end{frame}

%--------------------------------------------------
\begin{frame}
\frametitle{Encryption for chat sessions : OTR}
\begin{block}{OTR : Off-the-Record Messaging}
\begin{itemize}
\item Diffie-Hellman key exchange
\item off-the-record conversation
\item repudiable authentication by using message authentication codes.
\\(authentication ON | digital signature OFF)
\end{itemize}
\end{block}
Bob cannot prove that Alice generated the MAC.
Install Pidgin (cross-plateform) with plugin (available from the OTR homepage)
and start playing.
\end{frame}
%----------------------------------------------------
\begin{frame}
\frametitle{Encryption for disk}
Many possibilities, but full disk encryption is advised in case you really care
about privacy. For this purpose you have a plethora of choice.
\begin{itemize}
\item Stacked filesystem encryption (eCryptfs, EncFs, disk utility ...)
\item Disk encryption (dm-crypt, GELI, FileVault, DiskCryptor, trueCrypt ...)
\end{itemize}
\begin{block}{Case study : Plain dm-crypt}
\begin{itemize}
\item full disk encryption
\item bootloader and key on external device
\end{itemize}
\end{block}
(can also be done with Diskcryptor)
\end{frame}
%----------------------------------------------------
\begin{frame}
\frametitle{Encryption for smartphone}
\begin{block}{Android}
\begin{itemize}
\item Chatsecure (Facebook chat, GTalk, Jabber) [OTR Messaging]
\item Textsecure (SMS)
\item LUKS Manager (ROOT requiered)
\end{itemize}
\end{block}
\begin{block}{iOS}
\begin{itemize}
\item Chatsecure (Facebook chat, GTalk, Jabber) [OTR Messaging]
\item FDE available by default, bypass techniques available, proprietary
built system...\\ (More details : iPhone Forensic, O'Reilly)
\end{itemize}
\end{block}
\end{frame}
%----------------------------------------------------
\begin{frame}
\frametitle{Encryption for files}
\begin{block}{Mails : Use GPG}
\begin{itemize}
\item create your keys
\item share your public key
\item enter the \sout{matrix} Web Of Trust (WOT)
\item encrypt/sign your message and send it.
\item receive mails too.
\end{itemize}
\end{block}
\begin{block}{Files}
Basically you can do the same with 'regular file'...
Take care to not store keys near encrypted files, prefer symetrical encryption
if files will not be shared.
\end{block}
\end{frame}
